\bf Faster Neural Machine Translation Inference

### 2018-01-26 fast-beam/fast-beam.tex
fast beam paper

\documentclass[]{article}
\usepackage[letterpaper]{geometry}
\usepackage{amta2016}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{natbib}
\usepackage{layout}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}

@@

Firstly, the number of classes in many deep-learning applications is small. However, the number of classes in NMT models is typically in the tens or hundreds of thousands, corresponding to the vocabulary size of the output language. For example, ~\cite{sennrich-haddow-birch:2016:P16-12} experimented with target vocabulary size of 60,000 and 90,000 subword units. This makes the output layer of NMT models very computationally expensive. ??? shows the breakdown of amount of time during translation our NMT system; over 40\% of the time is involved in calculating the activation, softmax and the beam search. We will look at optimizations which explicitly target the output layer.

@@

Most current neural MT models follow an encoder-decoder architecture. The encoder calculates the word and sentence embeddings while the decoder generates the output sentence. The architecture within the encoder is still a subject of much research. ~\cite{kalchbrenner13emnlp} used a convolution to encode the input and a recurrent neural network (RNN) for the decoder. RNNs was used for both encoding and decoding in (??? who used RNN 1st). (???) significantly improved translation quality by using LSTM was used in each RNN node. ~\cite{D14-1179} used GRU that has the required properties of LSTM but is computationally cheaper. ~\cite{DBLP:journals/corr/BahdanauCB14} added attention model which improved translation at a cost of slower speed.

There has been recent attempts to move away from the sequence-to-sequence models of RNN encoder-decoder. Some justify their architecture on faster inference as well as better translation results. (??? Attention is all you need) and (??? course-to-fine) has been proposed as a fast alternatives to RNN-based models as it is possible to process more of the units in parallel.

@@

The output layer of most deep learning models consist of the following steps
\begin{enumerate}
   \item \vspace{-2 mm} activation - multiplication of the input with the weight matrix for that layer
   \item \vspace{-2 mm} addition of a bias term to the resulting scores
   \item \vspace{-2 mm} activation function - in the output layers, this is commonly softmax or a variant, eg. log-softmax.
   \item \vspace{-2 mm} a search for the argmax output class, and probability is necessary.
\end{enumerate}

@@

\begin{figure} [h]
\begin{algorithmic}
\REQUIRE activation vector $p$, bias vector $b$
\FORALL{$p_i$ in $p$}
  \STATE $p_i \gets p_i + b_i$
\ENDFOR 
\end{algorithmic}
\caption{Add Bias Term}
\label{algo:Add Bias Term}
\end{figure}

\begin{figure} [h]
\begin{algorithmic}
\REQUIRE activation vector $p$

@@

\STATE $sum \gets 0$ 
\FORALL{$p_i$ in $p$}
  \STATE $sum \gets sum + e^{p_i - max}$
\ENDFOR

@@

\FORALL{$p_i$ in $p$}
  \STATE $p_i \gets \frac{e^{p_i} - max}{sum} $
\ENDFOR

@@

\STATE $max \gets - \infty$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i > max$}
    \STATE $max \gets p_i$
    \STATE $argmax \gets i$
  \ENDIF
\ENDFOR

\RETURN $max$, $argmax$

@@

\STATE $max \gets - \infty$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i + b_i > max$}
    \STATE $max \gets p_i + b_i$
    \STATE $argmax \gets i$
  \ENDIF
\ENDFOR

@@

\STATE $sum \gets 0$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i > max$}
    \STATE $sum \gets sum + e^{p_i - max}$
  \ENDIF
\ENDFOR

\COMMENT{calculate softmax($p_i$)}
\RETURN $\frac{1}{sum}$, $argmax$

\end{algorithmic}
\caption{Combined softmax and argmax}
\label{algo:Fused Kernel}
\end{figure}

@@

 \section*{Acknowledgments}
This work is sponsored by the Air Force Research Laboratory, prime contract FA8650-11-C-6160.  The views and conclusions contained in this document are those of the authors and should not be interpreted as representative of the official policies, either expressed or implied, of the Air Force Research Laboratory or the U.S. Government.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2018}
\usepackage{times}
\usepackage{latexsym}

\usepackage[letterpaper]{geometry}
%\usepackage{amta2016}
\usepackage{url}
\usepackage{natbib}
\usepackage{layout}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{argmax}

@@

Firstly, the number of classes in many deep-learning applications is small. However, the number of classes in NMT models is typically in the tens or hundreds of thousands, corresponding to the vocabulary size of the output language. For example, ~\cite{sennrich-haddow-birch:2016:P16-12} experimented with target vocabulary sizes of 60,000 and 90,000 subword units. This makes the output layer of NMT models very computationally expensive. ??? shows the breakdown of amount of time during translation our NMT system; over 40\% of the time is involved in calculating the activation, softmax and the beam search. We will look at optimizations which explicitly target the output layer.

@@

Most current neural MT models follow an encoder-decoder architecture. The encoder calculates the word and sentence embeddings while the decoder generates the output sentence. The architecture within the encoder is still a subject of much research. ~\cite{kalchbrenner13emnlp} used a convolution to encode the input and a recurrent neural network (RNN) for the decoder. RNNs was used for both encoding and decoding in (??? who used RNN 1st). ~\cite{Sutskever:2014:SSL:2969033.2969173} significantly improved translation quality by using LSTM was used in each RNN node. ~\cite{D14-1179} used GRU that has the required properties of LSTM but is computationally cheaper. ~\cite{DBLP:journals/corr/BahdanauCB14} added attention model which improved translation at a cost of slower speed.

There has been recent attempts to move away from the sequence-to-sequence models of RNN encoder-decoder. Some justify their architecture on faster inference as well as better translation results. ~\cite{DBLP:journals/corr/VaswaniSPUJGKP17} and (??? course-to-fine) has been proposed as a fast alternatives to RNN-based models as it is possible to process more of the units in parallel.

@@

The output layer of most deep learning models consist of the following steps
\begin{enumerate}
   \item \vspace{-2 mm} multiplication of the input with the weight matrix $p = w x$
   \item \vspace{-2 mm} addition of a bias term to the resulting scores $p = p + b$
   \item \vspace{-2 mm} applying the activation function, most commonly softmax $ p_i = \exp(p_i) / \sum \exp(p_i) $
   \item \vspace{-2 mm} a search for the best output class, and probability if necessary $\argmax_i p_i$
\end{enumerate}

@@

\begin{figure} [h]
\begin{algorithmic}
\REQUIRE vector $p$, bias vector $b$
\FORALL{$p_i$ in $p$}
  \STATE $p_i \gets p_i + b_i$
\ENDFOR 
\end{algorithmic}
\caption{Add Bias Term}
\label{algo:Add Bias Term}
\end{figure}

\begin{figure} [h]
\begin{algorithmic}
\REQUIRE vector $p$

@@

\STATE $sum \gets 0$ 
\FORALL{$p_i$ in $p$}
  \STATE $sum \gets sum + \exp(p_i - max)$
\ENDFOR

@@

\FORALL{$p_i$ in $p$}
  \STATE $p_i \gets \frac{\exp(p_i) - max}{sum} $
\ENDFOR

@@

\STATE $max \gets - \infty$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i > max$}
    \STATE $max \gets p_i$
    \STATE $best \gets i$
  \ENDIF
\ENDFOR

\RETURN $max$, $best$

@@

\STATE $max \gets - \infty$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i + b_i > max$}
    \STATE $max \gets p_i + b_i$
    \STATE $best \gets i$
  \ENDIF
\ENDFOR

@@

\STATE $sum \gets 0$ 
\FORALL{$p_i$ in $p$}
  \IF{$p_i > max$}
    \STATE $sum \gets sum + \exp(p_i - max)$
  \ENDIF
\ENDFOR

\COMMENT{calculate softmax($p_i$)}
\RETURN $\frac{1}{sum}$, $best$

\end{algorithmic}
\caption{Fused softmax and argmax}
\label{algo:Fused Kernel}
\end{figure}

@@

%\section*{Acknowledgments}
%This work is sponsored by the Air Force Research Laboratory, prime contract FA8650-11-C-6160.  The views and conclusions contained in this document are those of the authors and should not be interpreted as representative of the official policies, either expressed or implied, of the Air Force Research Laboratory or the U.S. Government.
